Report on the Second Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE2)

### 2015-04-03 WSSSPE2_report/WSSSPE2_review.tex
Section 4: removed a TODO item done by Dan.
fix bib entry, adding note
Update WSSSPE2_review.tex
Lightning talk update

\note{Lead: Choi. Volunteers welcome.
\href{http://wssspe.researchcomputing.org.uk/wssspe2/lightning-talks/}{Slides}}
\todo{in the abstract and intro}

@@

@@

\choinote{Add missing speaker names}

@@

\\ Chris Lenhardt

>>>>

\note{Lead: Choi. Volunteers welcome.
\href{http://wssspe.researchcomputing.org.uk/wssspe2/lightning-talks/}{Slides.}}

@@

Venters proposed that technically sustainable software is a composite, first-class, non-functional requirement (NFR) 
that is at a minimum a measure of a systems maintainability and extensibility but may also include other NFR such as 
efficiency (energy and cost), interoperability, portability, reusability, scalability, and usability. To achieve 
technically sustainable software it was suggested that software architectures are fundamental as they are the primary 
carrier of system qualities (NFR) i.e. pre-system understanding, and influence how developers are able to understand, 
analyze, extend, test and maintain a software system i.e. post-deployment system understanding. In addition, it was 
highligted that the sustainability of software architectures also needs to be addressed to endure different types of 
change and evolution in order to mitigate architectural drift and erosion, and architectural knowledge vaporization.

@@

\choinote{Add missing speaker names} \katznote{they are all there}

@@

\\ Christopher Lenhardt
